5D de-aliased seismic data interpolation using non-stationary prediction error filter

### 2021-10-16 npef/paper.tex
Sat Oct 16 08:09:38 CDT 2021

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_obs5d-3}
   \label{fig:ha_obs5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_rr5d-3}
   \label{fig:ha_drr5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_recon5d-3}
   \label{fig:ha_npef5d}}\\
\caption{De-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
\label{fig:ha_obs5d,ha_drr5d,ha_npef5d}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-3-0}
%    \label{fig:r_obs5d}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-3-0}
%    \label{fig:r_drr5d}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-3-0}
%    \label{fig:r_npef5d}}\\
%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the damped rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
%	\label{fig:r_obs5d,r_drr5d,r_npef5d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zA}
%    \label{fig:r_obs5d1a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zB}
%    \label{fig:r_obs5d1b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zA}
%    \label{fig:r_drr5d1a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zB}
%    \label{fig:r_drr5d1b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zA}
%    \label{fig:r_npef5d1a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zB}
%    \label{fig:r_npef5d1b}}\\
%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Note the strong residual noise seen in (f) caused by the NPEF method. }
%	\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
%\end{figure}
%
%
%
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-4-0}
%    \label{fig:r_obs5d4}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-4-0}
%    \label{fig:r_drr5d4}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-4-0}
%    \label{fig:r_npef5d4}}\\
%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
%	\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
%\end{figure}
%
%
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zA}
%    \label{fig:r_obs5d2a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zB}
%    \label{fig:r_obs5d2b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zA}
%    \label{fig:r_drr5d2a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zB}
%    \label{fig:r_drr5d2b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zA}
%    \label{fig:r_npef5d2a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zB}
%    \label{fig:r_npef5d2b}}\\
%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Note the obviously more discontinuous events in (e) and (f) caused by the NPEF method.}
%	\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
%\end{figure}
%
%
%\begin{figure}[htb!]
%    \centering
%   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
%    \label{fig:ra_obs5d}}\\
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3-0}
%    \label{fig:ra_npef5d}}\\
%	\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. We treat the reconstructed data using the damped rank-reduction method as the starting data and further interpolate a trace every other traces in the $X$ and $Y$ directions. Each common offset cube has bee reshaped into a 2D matrix. (a) The regularly sampled data. Those blank areas denote missing traces. (b) Reconstructed data using the NPEF method. In this case of regularly missing traces, the rank-reduction method completely fails so we omit its result.}
%	\label{fig:ra_obs5d,ra_npef5d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3fk} %eps2pdf problem
%    \label{fig:ra_obs5d_new-3fk}}\\
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3fk}
%    \label{fig:ra_npef5d_new-3fk}}\\
%	\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. (a) The regularly sampled data before interpolation. (b) Reconstructed data using the NPEF method. }}
%	\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zA}
%    \label{fig:r_obs5da}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zB}
%    \label{fig:r_npef5db}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zA}
%    \label{fig:r_obs5da}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zB}
%    \label{fig:r_npef5db}}\\
%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
%	\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_obs}
%    \label{fig:os_obs}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_recon}
%    \label{fig:os_recon}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/ts_recon}
%    \label{fig:ts_recon}}
%	\caption{\new{Comparison between the two-step and one-step interpolation strategies. (a) Observed data when binned onto the regular grids of two times denser. (b) Reconstructed data by the one-step rank-reduction interpolation strategy. (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
%	\label{fig:os_obs,os_recon,ts_recon}
%\end{figure}
%
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zero2d}
%    \label{fig:zero2d}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d2}
%    \label{fig:recon2d2}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d}
%    \label{fig:recon2d}}\\
%	\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather. Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the rank-reduction method completely fails in this case.}}
%	\label{fig:zero2d,recon2d2,recon2d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zerofk2d}
%    \label{fig:zerofk2d}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d2}
%    \label{fig:reconfk2d2}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d}
%    \label{fig:reconfk2d}}\\
%	\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.  Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
%	\label{fig:zerofk2d,reconfk2d2,reconfk2d}
%\end{figure}
}

>>>>

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_obs5d-3}
   \label{fig:ha_obs5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_drr5d-3}
   \label{fig:ha_drr5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_recon5d-3}
   \label{fig:ha_npef5d}}\\
\caption{De-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
\label{fig:ha_obs5d,ha_drr5d,ha_npef5d}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_obs5d-3-0}
   \label{fig:r_obs5d}}\\
   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_drr5d-3-0}
   \label{fig:r_drr5d}}\\
   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_npef5d-3-0}
   \label{fig:r_npef5d}}\\
\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the damped rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
\label{fig:r_obs5d,r_drr5d,r_npef5d}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cog-zA}
   \label{fig:r_obs5d1a}}
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cog-zB}
   \label{fig:r_obs5d1b}}\\
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cog-zA}
   \label{fig:r_drr5d1a}}
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cog-zB}
   \label{fig:r_drr5d1b}}\\
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cog-zA}
   \label{fig:r_npef5d1a}}
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cog-zB}
   \label{fig:r_npef5d1b}}\\
\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Note the strong residual noise seen in (f) caused by the NPEF method. }
\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_obs5d-4-0}
   \label{fig:r_obs5d4}}\\
   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_drr5d-4-0}
   \label{fig:r_drr5d4}}\\
   \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d/Fig/r_npef5d-4-0}
   \label{fig:r_npef5d4}}\\
\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cmg-zA}
   \label{fig:r_obs5d2a}}
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_obs5d-cmg-zB}
   \label{fig:r_obs5d2b}}\\
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cmg-zA}
   \label{fig:r_drr5d2a}}
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_drr5d-cmg-zB}
   \label{fig:r_drr5d2b}}\\
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cmg-zA}
   \label{fig:r_npef5d2a}}
   \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d/Fig/r_npef5d-cmg-zB}
   \label{fig:r_npef5d2b}}\\
\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Note the obviously more discontinuous events in (e) and (f) caused by the NPEF method.}
\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
\end{figure}

\begin{figure}[htb!]
   \centering
  \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_obs5d_new-3-0}
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
   \label{fig:ra_obs5d}}\\
   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_npef5d_new-3-0}
   \label{fig:ra_npef5d}}\\
\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. We treat the reconstructed data using the damped rank-reduction method as the starting data and further interpolate a trace every other traces in the $X$ and $Y$ directions. Each common offset cube has bee reshaped into a 2D matrix. (a) The regularly sampled data. Those blank areas denote missing traces. (b) Reconstructed data using the NPEF method. In this case of regularly missing traces, the rank-reduction method completely fails so we omit its result.}
\label{fig:ra_obs5d,ra_npef5d}
\end{figure}

\begin{figure}[htb!]
   \centering
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_obs5d_new-3-0}
   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_obs5d_new-3fk} %eps2pdf problem
   \label{fig:ra_obs5d_new-3fk}}\\
   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d/Fig/r_npef5d_new-3fk}
   \label{fig:ra_npef5d_new-3fk}}\\
\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. (a) The regularly sampled data before interpolation. (b) Reconstructed data using the NPEF method. }}
\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zA}
   \label{fig:r_obs5da}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_obs5d_new-cog-zB}
   \label{fig:r_npef5db}}\\
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zA}
   \label{fig:r_obs5da}}
   \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d/Fig/r_npef5d_new-cog-zB}
   \label{fig:r_npef5db}}\\
\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_obs}
%    \label{fig:os_obs}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/os_recon}
%    \label{fig:os_recon}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_onestep/Fig/ts_recon}
%    \label{fig:ts_recon}}
%	\caption{\new{Comparison between the two-step and one-step interpolation strategies. (a) Observed data when binned onto the regular grids of two times denser. (b) Reconstructed data by the one-step rank-reduction interpolation strategy. (c) Reconstructed data by the two-step rank-reduction and NPEF interpolation strategy.}  }
%	\label{fig:os_obs,os_recon,ts_recon}
%\end{figure}
%
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zero2d}
%    \label{fig:zero2d}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d2}
%    \label{fig:recon2d2}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/recon2d}
%    \label{fig:recon2d}}\\
%	\caption{\new{De-aliased interpolation results of the second field data example for a common shot gather. Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the rank-reduction method completely fails in this case.}}
%	\label{fig:zero2d,recon2d2,recon2d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/zerofk2d}
%    \label{fig:zerofk2d}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d2}
%    \label{fig:reconfk2d2}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{simple3da/Fig/reconfk2d}
%    \label{fig:reconfk2d}}\\
%	\caption{\new{FK spectra of de-aliased interpolation results of the second field data example.  Each gather has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
%	\label{fig:zerofk2d,reconfk2d2,reconfk2d}
%\end{figure}
}
